% template by zmanji/zameermanji.com
\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[stretch=10]{microtype}
\usepackage{hyperref}
\usepackage{tgpagella}
\usepackage{enumitem}
\usepackage{indentfirst}

\pagestyle{empty}

\linespread{1}
\begin{document}
\fontsize{9.2}{11.5}\selectfont

\begin{center}
{\Large \textbf{Santi Santichaivekin}}

\ \ \href{mailto:jsantichaivekin@hmc.edu}{jsantichaivekin@hmc.edu}\ \ 
\ \ \textbullet
\ \ \href{https://github.com/ssantichaivekin}{github.com/ssantichaivekin}
\ \ \textbullet
\ \ (+66)89-449-7044

\end{center}


\hrule
\vspace{-0.95em}
\subsection*{Education}
  \begin{itemize}
    \parskip=-0.5em

    % Harvey Mudd College
    \item[]
    \textbf{Harvey Mudd College} \hfill
      Claremont, CA\\
    {B.S. in Computer Science, GPA 3.81
    \hfill \emph{Class of 2022}}
  \end{itemize}
  \vspace{-2.2em}
\subsection*{Coursework}
\begin{itemize}
\item[]
    \parskip=-0.2em
  % \textbf{In progress:}   \\
  % \textbf{Completed:}
  Advanced Topics in Algorithms; 
  Complexity Theory;
  Machine Learning and Search; 
  Digital Electronics; 
  Science of Debugging;
  Computer Systems;
  Software Development;
  Phylogenic Tree Reconstruction;
  Multivariable Calculus;
  Differential Equations;
  Linear Algebra
  

\end{itemize}

\hrule
\vspace{-0.95em}
\subsection*{Skills}
\begin{itemize}
\item[]
    \parskip=-0.2em
  Proficient: Python | Knowledgeable: Go, Java, C++, C, C\#, JavaScript, React, Bash, Prolog, System Verilog, debugging with recordings,
  distributed systems
    
\end{itemize}

\hrule
\vspace{-0.95em}
\subsection*{Experience}
  \begin{itemize}
    \item[]
    \parskip=-0.2em
    {\textbf{Research Assistant}, \textit{Harvey Mudd College}, Claremont, CA \hfill {Summer 2020}}
    \begin{itemize}[label=\textbullet]
      \itemsep0.1em
      \item Managed a team of six under professor supervision to develop Empress---a Python application that helps biologists understand how different species lived together in the past. (\href{https://github.com/ssantichaivekin/empress}{github.com/ssantichaivekin/empress})
      \item Made key design and style decisions, managed GitHub issues, led rigorous code review processes.
      \item Created a pipeline for testing, freezing, and packaging the application using Pyinstaller and Github Actions.
      \item Held Zoom information sessions on Git, GitHub, text editors and integrated development environments, Python best practices, and Python debugging tools for rising sophomores in the team.
    \end{itemize}
    \vspace{0.1em}
    \item[]
    {\textbf{CS Tutor/Grader}, \textit{Harvey Mudd College}, Claremont, CA \hfill {Spring 2018 - Fall 2020}}
    \begin{itemize}[label=\textbullet]
      \itemsep0.1em
      \item Tutored and graded Advanced Algorithms class which covers randomized algorithms, approximation algorithms, competitive algorithms, duality, matroid theory, advanced data structures and analysis.
      \item Tutored and graded Computability and Logic class which covers proof methods, automata, Prolog, and computability theory. Wrote autograder for Prolog using Python subprocess module and Swipl compiler.
      \item Tutored and graded CS For Insight class which focused 
      on using Python libraries for everyday tasks such as file management, web-scraping, 
      machine learning, and HTML generation.
    \end{itemize}
    \vspace{0.1em}
    \item[]
    {\textbf{Software Engineer Intern}, \textit{Uber ATG}, San Francisco, CA \hfill {Summer 2019}}
    \begin{itemize}[label=\textbullet]
      \itemsep0.1em
      \item Implemented an algorithm to help reduce the number of
      latitude-longitude waypoints in routing engine for self-driving cars. Used Java.
      \item Developed metrics for measuring the consistency of self-driving car constraints such as "do not take unprotected left turn" and "do not enter school area" among different services in Uber's self-driving platform. Used Go.
    \end{itemize}
    \vspace{0.1em}
    \item[]
    {\textbf{Software Engineer Intern}, \textit{Microsoft}, Bellevue, WA \hfill {Summer 2018}}
    \begin{itemize}[label=\textbullet]
      \itemsep0.1em
      \item Implemented an event queue which performs layout calculations in the background 
      across multiple frames to make complex visual transitions in Microsoft Whiteboard application
      more responsive. Used C\#.
    \end{itemize}
    % \vspace{0.1em}
    % \item[]
    % {\textbf{Team Leader}, \textit{Thailand National Software Contest 2016}, Bangkok, Thailand \hfill {Spring 2016}}
    % \begin{itemize}[label=\textbullet]
    %   \itemsep0.1em
    %   \item Designed a system for Thai word segmentation using maximum dictionary matching and exhaustive 
    %   search in JavaScript.
    %   \item Deployed a web application to analyze the analyze rythms, sounds, rhymes, and alliterations of Thai 
    %   poems using the International Phonetic Alphabet (IPA).
    % \end{itemize}


  \end{itemize}

\hrule
\vspace{-0.95em}
\subsection*{Publications}
\begin{itemize}[label={}]
  \parskip=-0.45em
  \item Santichaivekin, S., Yang, Q., Liu, J., Mawhorher, R., Jiang, J., Wesley, T., Wu, Y., \& Libeskind-Hadas, R. \textit{eMPRess: A Systematic Cophylogeny Reconciliation Tool}. Accepted for publication on Bioinformatics.
  \vspace{0.2em}
  \item Santichaivekin, S., Mawhorter, R., \& Libeskind-Hadas, R. \textit{An efficient exact algorithm for computing all pairwise distances between reconciliations in the duplication-transfer-loss model.} \href{https://doi.org/10.1186/s12859-019-3203-9}{BMC Bioinformatics 20, 636 (2019)}.
\end{itemize}

  
\hrule
\vspace{-0.95em}
\subsection*{Personal Projects}
  \begin{itemize}
    \parskip=-0.45em
    \item[]
    {\textbf{Halite3 AI Competition Bot} (\href{https://github.com/ssantichaivekin/halite3}
    {github.com/ssantichaivekin/halite3})\hfill {Fall 2018}}
    \begin{itemize}[label=\textbullet]
        \item  Wrote evaluation functions navigate ships around the game map and collect resources without colliding.
        Used Python and switched to C++ for performance.
        \item Used Evolutionary Algorithm in Python to fine-tune hyperparameters on DigitalOcean server.
        \item Finished with rank 201 out of 4014 total participants.
    \end{itemize}
  \end{itemize}

\hrule
\vspace{-0.95em}
\subsection*{Honors and Awards}
  \begin{itemize}
    \parskip=-0.5em
    % Twitter 2.0
    \item[]
    {5\textsuperscript{th} place in ACM-ICPC Contest SoCal Region, 2018}\\
    {5\textsuperscript{th} place in ACM-ICPC Contest SoCal Region, 2017}\\
    {1\textsuperscript{st} place in Harvey Mudd College Microsoft Coding Competition, 2017}
  \end{itemize}

% \hrule
% \vspace{-1.0em}
% \subsection*{Hobbies}
% \begin{description}[labelindent=\parindent]
%   \parskip=-0.5em
% \item[] {Unicycle, Competitive Programming, Drawing, Painting, Subtitling Educational Videos.}
% \end{description}

\end{document}
